Growing up with Nell: A Narrative Interface for Literacy

### 2012-03-10 paper.tex
Reformat and trim the story module example.

\subsection{Rule-based story modules}
Narrative is the core of the Nell interface.  It is important that
Nell's story be modular and extensible.  We use a rule-based story
model with programmable conflict resolution to provide this ability.
Figure~\ref{fig:rules} shows an excerpt of the story module driving
the interaction described in the introduction to this paper.

@@

\begin{figure}
\begin{verbatim}
<aiml version="1.0">
<category>
 <pattern>GO *</pattern>
 <template><srai><star/></srai></template>
</category>

@@

<category>
 <pattern>NORTH</pattern>
 <template>
  <javascript>FireEvent(Chat, "NORTH")</javascript>
 </template>
</category>
</aiml>
\end{verbatim}
\caption{An AIML fragment which recognizes the commands ``N'',
  ``North'', and ``Go North''.}\label{fig:aiml}
\end{figure}
% show fragment
Each story module can include AIML fragments extending the
conversational capabilities of Nell's agents.  Figure~\ref{fig:aiml}
illustrates how this can be used to implement a traditional
text adventure interaction for a particular story module.
The child can write instructions such as, ``go north,'' ``go
east,'' or ``open door'' for the agent.  These trigger events
handled by the story module to move the agent through the
adventure---for example, by causing the activity to draw a
new location, causing the agent to describe it, and shifting the
AIML topic to enable vocabulary suitable for the new location.

>>>>

\subsection{Rule-based story modules}
\begin{figure}\small
\begin{verbatim}
{ world: { // id gives canonical URL for this module
    id: "/nell.laptop.org/chapters/alphabet-book"
    scene: "opening", // initial scene
  }, scenes: [
    { id: "opening", subject: "actors/princess",
      verb: "speak", object: "actors/user",
      text: "Hello! Would (o/2) like to hear a story?"
    },
    { id: "story-1",
      cond: rule`At(opening) && Event(Chat, Yes)`,
      subject: "actors/princess",
      verb: "speak", object: "actors/user",
      text: "Once upon a time..." },
    ...
    { id: "r-drawn",
      cond: rule`Event(Activity, DrawR)`,
      subject: "actors/princess",
      verb: "speak", object: "actors/user",
      text: "Very good, (o/3)!",
      action: js`startAnimation("r-runs")` },
    ...
  ], ... }
\end{verbatim}
\caption{Excerpt of story module.  JSON syntax has been extended with
quasiquote~\cite{quasiquote}.}\label{fig:rules}
\end{figure}
Narrative is the core of the Nell interface.  It is important that
Nell's story be modular and extensible.  We use a rule-based story
model with programmable conflict resolution to provide this ability.
Figure~\ref{fig:rules} shows an excerpt of the story module driving
the interaction described in the introduction to this paper.

@@

\begin{figure}\small
\begin{verbatim}
<aiml version="1.0">
<category>
 <pattern>GO *</pattern>
 <template><srai><star/></srai></template>
</category>

@@

<category>
 <pattern>NORTH</pattern>
 <template>
  <javascript>FireEvent(Chat, "North")</javascript>
 </template>
</category>
</aiml>
\end{verbatim}
\caption{An AIML fragment which recognizes the commands ``N'',
  ``North'', and ``Go North''.}\label{fig:aiml}
\end{figure}
% show fragment
Each story module can include AIML fragments extending the
conversational capabilities of Nell's agents.  Figure~\ref{fig:aiml}
illustrates how this can be used to implement a traditional
text adventure interaction for a particular story module.
The child can write instructions such as, ``go north,'' ``go
east,'' or ``open door'' for the agent.  These trigger events
handled by the story module to move the agent through the
adventure---for example, by causing the activity to draw a
new location, causing the agent to describe it, and shifting the
AIML topic to enable vocabulary suitable for the new location.
